### 2013-03-15 eusflat2013/introduction.tex
Another update that adds a few things and dots the i's and crosses the t's in the abstract and sections 1, 2 and 3.

%1. Introduction
Information systems (IS) in general and database systems (DS) in particular have always tried to model parts of reality. To achieve this modelling, such systems contain data representing properties of real-world objects or concepts. As time is an essential aspect of many of these, information systems often contain data representing temporal notions which describe their temporal properties. Such temporal notions usually take the form of either instants (time points)~\cite{Dyreson1994},~\cite{Jensen1998} or time intervals~\cite{Dyreson1994},~\cite{Jensen1998}.
%TODO: more references in the above part?

Data are often produced by humans, but human-made data are prone to imperfections: some data may be vague, imprecise, incomplete, contradictory or uncertain. Data representing temporal notions may contain such uncertainties too.

Generally, one of the most important purposes of an IS is to allow the retrieval of information or knowledge deduced from its data. Information or knowledge is usually retrieved from an IS by querying its contents and examining the query results or by visualizing its contents, querying this visualization and examining these query results.
%TODO: include some form of proof or previous work with these statements!

Of course, when temporal information is contained in an IS, it can be used in the querying process. Usually, querying an IS containing data representing temporal notions is done by specifying one or more time indications and requesting information that is related to these notions, where the nature and semantics of these relationships are specifically temporal. Thus, specific temporal relationships are necessary. Notably, Allen~\cite{Allen1983} presented a reasoning framework containing all semantically usefull basic temporal relationships between time intervals (and as a special case instants). The resulting Allen relationships are shown in figure \ref{fig:allen-relationships}.

To be able to query IS and DS containing uncertain data representing uncertain time indications, a framework is necessary, able to represent uncertainties in time indications without (much) information loss and able to temporally reason with such uncertain time indications. Although many proposals for such frameworks exist, the work presented in this paper focusses on two: the \emph{ill-known constraint \emph{(IKC)} framework}~\cite{Pons2011} and the \emph{triangular model \emph{(TM)} framework}~\cite{DeTre2012}.

The work presented in this paper consists of a comparison of the approaches, used by both frameworks, to representing time intervals subject to uncertainty and to reasoning about the temporal relationships between such intervals and perfectly defined time intervals.

The structure of this paper is as follows: section \ref{sec:general-preliminaries} presents some general preliminaries and naming and notation conventions used in this paper. Sections \ref{sec:ikc} and \ref{sec:tm} introduce the IKC and TM frameworks respectively: both sections first introduce some preliminary concepts and techniques specific to the framework under consideration, then explain how the representation of time intervals is done and finally show how the evaluation of Allen relationships between a crisp interval and one subject to uncertainty is done. In section \ref{sec:proposal}, both frameworks are compared: first their approaches to representing time intervals are compared, next their approaches to evaluating Allen relationships are compared. Finally, section \ref{sec:conclusions} presents the principal conclusions of the presented work and some possible future work.

>>>>

Information systems (IS) have always tried to model parts of reality. To achieve this modelling, such systems contain data representing properties of real-world objects or concepts. As time is an essential aspect of many real-world objects or concepts, information systems often contain data representing temporal notions which describe such temporal properties. Such temporal notions usually take the form of either instants~\cite{Dyreson1994},~\cite{Jensen1998}, which can informally be seen as infinitely short `moments' or `points' in time, or time intervals~\cite{Dyreson1994},~\cite{Jensen1998}.

Data are often produced by humans, but human-made data are prone to imperfections: some data may be vague, imprecise, incomplete, contradictory or uncertain. Data representing temporal notions may contain such imprecisions too. The work presented in this paper is specifically concerned with time intervals (and as a special case: instants) subject to uncertainty.

Generally, one of the most important purposes of an IS is to allow the retrieval of information or knowledge deduced from its data. Information or knowledge is usually retrieved from an IS by querying it and examining or analyzing the query results or by visualizing the contents of the IS, querying this visualization and examining or analyzing the resulting visualization(s).

Of course, when temporal information is represented in an IS, querying this IS may have a temporal aspect too. Usually, querying an IS containing data representing temporal notions is conceptually done by specifying one or more time indications and requesting information that is in a specific relationship with these indications, where the semantics of these relationships are specifically temporal. Thus, some existing proposals have considered groups of basic relationships between time indications used to construct and express specific temporal relationships. Notably, Allen~\cite{Allen1983} presented a reasoning framework containing all semantically usefull basic temporal relationships between time intervals (and as a special case instants). The resulting relationships are shown in figure \ref{fig:allen-relationships}. These Allen relationships are used in the presented work.

To be able to query IS containing data representing time indications subject to uncertainty, a framework is necessary, able to represent uncertainties in time indications in a semantically sound way, without (much) information loss and able to temporally reason with such time indications in a semantically sound and usefull way. Although more proposals for such frameworks exist, the work presented in this paper focusses on just two: the \emph{ill-known constraint \emph{(IKC)} framework}~\cite{Pons2011} and the \emph{triangular model \emph{(TM)} framework}~\cite{DeTre2012}.

The work presented in this paper consists of a comparison of both frameworks, about the approaches they use to represent time intervals subject to uncertainty and to reason about the temporal relationships between such intervals and time intervals without uncertainty.

The structure of this paper is as follows: section \ref{sec:general-preliminaries} presents some general preliminaries and naming and notation conventions used in this paper. Sections \ref{sec:ikc} and \ref{sec:tm} introduce the IKC and TM frameworks respectively: both sections first introduce some preliminary concepts and techniques specific to the framework under consideration, then explain how the representation of time intervals by the framework is done and finally show how the evaluation of Allen relationships between an interval subject to uncertainty and one without uncertainty is done. In section \ref{sec:proposal}, both frameworks are compared: first their approaches to representing time intervals are compared, next their approaches to evaluating Allen relationships are compared. Finally, section \ref{sec:conclusions} presents the principal conclusions of the presented work and some possible future work.

%TODO: more references in the above part?
%TODO: include some form of proof or previous work with these statements?!
